%-------------------------
% Resume in Latex
% Initial Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemWithMoreVSpace}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-0.5pt}}
  }
}
\newcommand{\resumePoint}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubheadingExtended}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#5}
    \end{tabular*}\vspace{-12pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-4pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeInnerItemListStart}{\begin{itemize}\vspace{-1pt}}
\newcommand{\resumeInnerItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nikhil-sulegaon/}{\Huge Nikhil Sulegaon}} & \faMapMarker \enspace 2995 Glenwood Dr APT 113 Boulder CO USA 80301\\[3pt]
   \href{https://github.com/nikhilsu}{\faGithub \enspace https://github.com/nikhilsu} & \faEnvelopeO \enspace \href{mailto:nisu8311@colorado.edu}{nisu8311@colorado.edu} \\
   \href{https://www.linkedin.com/in/nikhil-sulegaon/}{\faLinkedin \enspace https://www.linkedin.com/in/nikhil-sulegaon/} & \faPhone \enspace \href{tel:+1-720-491-9222}{+1-720-491-9222}
  
\end{tabular*}\vspace{-8pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {University of Colorado Boulder}{Boulder, CO}
      {Master of Science in Computer Science;  GPA: 3.8/4.0}{Aug 2017 -- Present (Expected: May 2019)}
      {Relevant courses: Machine Learning, NLP, Object Oriented Analysis and Design, and Computer Vision.}
    \resumeSubheadingExtended
      {BMS College of Engineering}{Bangalore, India}
      {Bachelor of Engineering in Information Science and Engineering;  GPA: 8.92/10.0}{Sep 2011 -- May 2015}
      {Relevant courses: Data Structures using C, Design and Analysis of Algorithms, Operating Systems and Databases}
  \resumeSubHeadingListEnd\vspace{6pt}


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \setlength\itemsep{0em}
    \item{
     \textbf{Languages}{: Python, C\#, Java, Ruby, C++, C, PHP, and NodeJs.}
    }
    \item{
     \textbf{Frameworks}{: Keras, Theano, Tensorflow, ASP.NET, Flask, Ruby on Rails, SpringMVC, ReactJs with Redux.}
    }
    \item{
     \textbf{Databases}{: MS SQL Server, Postgres, MySQL, and MongoDB.}
    }
    \item{
     \textbf{Others}{: Android, Git, AWS, Heroku, CI, Docker, HTML/CSS, JavaScript, Shell scripting, and Powershell.}
    }\vspace{-5pt}
 \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}{Boulder, CO}
      {Teaching Assistant - Software tools and methodologies}{Sep 2017 - Present}
      \resumeItemListStart
          \resumePoint{Teaching 60 students, full stack development and deployment of applications using core Agile principles and TDD.
          }
          \resumePoint{Training students on technologies like Shell Scripting, HTML/CSS, JS, Git, REST, MySQL, PHP, CI, and Heroku.
          }
          \resumePoint{This position also involves guiding and advising students on their academic and personal projects.
          }
      \resumeItemListEnd
    \resumeSubheading
      {ThoughtWorks - \normalfont A staunch Agile company focused on quality of its deliverables}{Bangalore, India}
      {Application Developer}{Aug 2015 - Aug 2017}
      \resumeItemListStart
        \resumeItem {Project Management Tool(C\#, Silverlight, ASP.NET)}
          {A Multi-tenant SaaS Application having about 2000 tenants and 2000-5000 users per tenant in production.
          \resumeInnerItemListStart
            \resumePoint {Worked on building a robust backend through Test Driven Development using C\#.}
            \resumePoint {Refactored the legacy code base and increased the test coverage from 16\% to 65\%.}
            \resumePoint {Optimized complex SQL queries to improve performance of key features by around 80\%.}
          \resumeInnerItemListEnd}
        \resumeItemWithMoreVSpace {Food-Supplies Management(Python, Sklearn, Keras)}{A stock management tool to help the pantry of the office plan the supply of fruits, vegetables, and grocery in order to minimize wastage of food.}
        \resumeItem{Danglay(Ruby, Ruby on Rails)}{A scalable carpooling web application using Ruby on Rails to solve the problem of commute faced by numerous employees at ThoughtWorks.}
      \resumeItemListEnd
    \resumeSubheading
      {FreeLancing - \normalfont{Embedded System Prototyping}}{Bangalore, India}
      {Designed electronic prototypes of various Assistive Technology and Home Automation devices.}{Oct 2014 - June 2015}
      \resumeItemListStart
          \resumeItem{EMG Controlled Wheelchair(Arduino, C)}{A wheelchair which was controlled by an electromyograph, aimed at helping paraplegic patients move around. This system could also be controlled by a voice recognition unit.}
          \resumeItem{Surveillance System(Java, Android, Python, C)}{Security system that enabled the owner to control the entrance gates and lockdown the house. This system also provided live surveillance of the house on a smart-phone.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Agile board(Java, SpringMVC)}
      {Developed an Agile board for an OOP-design cum refactoring exercise. The backend was implemented by incorporating various Design Patterns and best practices of Java, SpringMVC, and OOP. Also introduced a \href{https://github.com/nikhilsu/Agile-board/blob/master/src/main/java/com/prorg/helper/result/Response.java}{\emph{custom design pattern}}. \textbf{Links:}
      \href{https://prorg.herokuapp.com}{\textit{App}}, \href{https://github.com/nikhilsu/Agile-board}{\textit{GitHub}}.}
    \resumeSubItem{Object 3D Pose Estimation(Python, Tensorflow, C\#, Unity)}
      {Using Neural Nets to deduce a dynamic object\rq s 3D location(x, y, z) and rotation(roll, pitch, yaw). This information is piped to an AR head-mounted display to generate real and virtual object interactions. \textbf{Links:}
      \href{https://drive.google.com/file/d/1kCepKQxR73tUTLuvmd1YL3sIbj1GxDdc/view?usp=sharing}{\textit{Demo}}, \href{https://drive.google.com/file/d/1mRwSJ8p2-g-gtBGl1A8seRB8SojWQphm/view?usp=sharing}{\textit{Paper(Report)}}, \href{https://github.com/nikhilsu/Object-location-detection}{\textit{GitHub}}.}
    \resumeSubItem{Navisys(Java, Android, Python, C++, OpenCV)}
      {Designed an embedded system, fitted into a wearable jacket, that provided turn-by-turn navigation with dynamic obstacle detection to visually impaired users.  Output from the Ultrasonic sensors and image feed from a webcam was used to localize an obstacle. \textbf{Links:}
      \href{https://drive.google.com/file/d/1bFHeZ7-7uwZ0spir3YQ7r0maWdLteEtu/view?usp=sharing}{\textit{Report}},
      \href{https://drive.google.com/file/d/1JWB67U2jjTG7cXZFVjRPVGKsv-rRhgUQ/view?usp=sharing}{\textit{Synopsis}}.}
    \resumeSubHeadingListEnd

\section{Achievements}
  \resumeSubHeadingListStart
    \resumePoint{Won the 'Best Research Project' award at the IEEE International Advance Computing Conference 2015, held at B.M.S College of Engineering. The project also featured in the \href{https://drive.google.com/open?id=0B0vNhKZyi8qyam1fQ3lfaE1hMkE}{\emph{local newspaper(link)}} for its novel approach of implementation.}
  \resumeSubHeadingListEnd
\end{document}