%-------------------------
% Resume in Latex
% Initial Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xifthen}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \linespread{1}
	\item\small{
    	\textbf{#1}{: #2}
  	}
}

\newcommand{\resumePoint}[1]{
	\item\small{#1}
}

\newcommand{\resumeExperienceSubheading}[5]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \normalfont{\small#2} - \textbf{#3}\normalfont{#4} & #5 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingExtended}[7]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} in \textit{#4}; \textbf{#5} & \textit{\small #6} 
    \end{tabular*}
    \ifthenelse{\isempty{#7}}%
    {}% if #1 is empty
    {\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#7}
    \end{tabular*}
    \vspace{-5pt}}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-12pt}}
\newcommand{\resumeProjectItemListStart}{\begin{itemize}[leftmargin=*]\vspace{-4pt}}
\newcommand{\resumeProjectItemListEnd}{\end{itemize}\vspace{-2pt}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeInnerItemListStart}{\begin{itemize}\vspace{-1pt}}
\newcommand{\resumeInnerItemListEnd}{\end{itemize}\vspace{2pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nikhil-sulegaon/}{\Huge Nikhil Sulegaon}} & \faMapMarker \enspace 2995 Glenwood Dr APT 113 Boulder CO USA 80301\\[3pt]
   \href{https://github.com/nikhilsu}{\faGithub \enspace https://github.com/nikhilsu} & \faEnvelopeO \enspace \href{mailto:nisu8311@colorado.edu}{nisu8311@colorado.edu} \\
   \href{https://www.linkedin.com/in/nikhil-sulegaon/}{\faLinkedin \enspace https://www.linkedin.com/in/nikhil-sulegaon/} & \faPhone \enspace \href{tel:+1-720-491-9222}{+1-720-491-9222}
   \vspace{-7pt}
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {University of Colorado Boulder}{Boulder, CO}
      {Master of Science}{Computer Science}{GPA: 3.8/4.0}{Aug 2017 -- Present (Expected: May 2019)}
      {Relevant courses: Machine Learning, NLP, Probabilistic Models for ML, Computer Vision, and Big Data Architecture}
    \resumeSubheadingExtended
      {BMS College of Engineering}{Bangalore, India}
      {Bachelor of Engineering}{Information Science and Engineering}{GPA: 8.92/10.0}{Sep 2011 -- May 2015}
      {}
  \resumeSubHeadingListEnd
\vspace{-2pt}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \setlength\itemsep{0em}
    \item{
     \textbf{Languages}{: Python, C\#, Java, Ruby, C++, C, MATLAB,  MS SQL Server, Postgres, MySQL, \& MongoDB..}
    }
    \item{
     \textbf{Frameworks}{: Tensorflow, Keras, ASP.NET, Ruby on Rails, SpringMVC.}
    }
    \item{
    \textbf{Data Science}}{: Neural Networks, KNN, SVM, KMeans, LSTM, Linear Regression, and, Probabilistic models.
    }
 \resumeSubHeadingListEnd

%

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Object 3D Pose Estimation (Python, Tensorflow, C\#, Unity) {Links:}
      \href{https://drive.google.com/file/d/1kCepKQxR73tUTLuvmd1YL3sIbj1GxDdc/view?usp=sharing}{\normalfont{\textit{Demo}}}, \href{https://drive.google.com/file/d/1mRwSJ8p2-g-gtBGl1A8seRB8SojWQphm/view?usp=sharing}{\normalfont{\textit{Paper}}}, \href{https://github.com/nikhilsu/Object-location-detection}{\normalfont{\textit{GitHub}}}}{
      \resumeProjectItemListStart
        \resumePoint{Using a CNN to predict an object\rq s 3D pose using its image to create real and virtual object interactions in a Hololens.}
        \resumePoint{Tweaked the CNN to use a custom Tukey's Biweight Loss function thereby achieving a test accuracy of 95\%.
        }
      \resumeProjectItemListEnd
    }
    \resumeSubItem{Deception Detection in hotel reviews (Python, Sklearn, NLTK)}{
        \resumeProjectItemListStart
          \resumePoint{Implemented a Naive Bayes model and an SVM to detect deceptive or fake hotel reviews using a small dataset. }
          \resumePoint{An SVM with Feature Engineering techniques achieved an accuracy of 64\% with a standard deviation of 5.2\%.
          }
        \resumeProjectItemListEnd
    }
    \resumeSubItem{Navisys (Java, Android, Python, C++, OpenCV) Links:
      \href{https://drive.google.com/file/d/1bFHeZ7-7uwZ0spir3YQ7r0maWdLteEtu/view?usp=sharing}{\normalfont{\textit{Report}}},
      \href{https://drive.google.com/file/d/1JWB67U2jjTG7cXZFVjRPVGKsv-rRhgUQ/view?usp=sharing}{{\normalfont{\textit{Synopsis}}}.}}
      {
        \resumeProjectItemListStart
          \resumePoint{An embedded system fitted into a jacket that provides turn-by-turn navigation to the visually impaired.}
          \resumePoint{Jacket also detected humans and obstacles using Ultrasonic sensors, \& Image processing techniques of Haar Cascades.
          }
        \resumeInnerItemListEnd
      }\vspace{-2pt}
    \resumeSubItem{Named Entity Recognition (Python, Sklearn, NLTK)}{
        \resumeProjectItemListStart
          \resumePoint{Achieved 93\% Accuracy and a 52\% F1 measure  when using a Perceptron to perform NER tagging of a sentence.}
          \resumePoint{Implemented an HMM as a baseline model that was batch-trained by chuncking data due to large size of dataset.
          }
        \resumeProjectItemListEnd
    }
    \resumeSubItem{Handwritten Number Recognition (Python, Keras)}{
        \resumeProjectItemListStart
          \resumePoint{Used KNN(acc: 96\%), SVM(acc: 97\%), and CNN(acc: 98\%) models to recognize handwritten numerals.
          }
          \resumePoint{Different models were compared based on accuracy, precision, etc, using Cross Validation and L2 regularization.}
        \resumeProjectItemListEnd
    }
    \resumeSubItem{Sentiment Analysis of Movie Reviews using IMDB dataset (Python, Keras)}{
        \resumeProjectItemListStart
          \resumePoint{Used Naive bayes with Laplace smoothing, SVM and RNNs to compare and contrast the performance of each model.
          }
          \resumePoint{Also analyzed and compared LSTMs and GRU for sequential prediction with pre-trained word embeddings (GloVe).
          }
        \resumeProjectItemListEnd
    }
    \resumeSubHeadingListEnd
\vspace{3pt}
%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeExperienceSubheading
      {Teaching Assistant}{\href{https://www.colorado.edu/cs/csci-3308-software-development-methods-and-tools}{(S/W Dev Methods \& Tools)}}{University of Colorado Boulder}{}{Sep 2017 - Present}
      \resumeItemListStart
        \vspace{2pt}
          \resumePoint{Teaching 60 students, full stack development and deployment of applications using core Agile principles and TDD.
      }
      \vspace{-2pt}
      \resumeItemListEnd
    \resumeExperienceSubheading
      {Application Developer}{}{ThoughtWorks}{, Bangalore, India}{Aug 2015 - Aug 2017}
      \resumeItemListStart
      \resumeItem {Food-Supplies Management - PoC (Python, SVM, Keras)}
        {\resumeInnerItemListStart
          \vspace{2pt}
            \resumePoint{A tool built using ML, used to plan the amount of food to be prepared in order to reduce wastage in the office.}
          \resumeInnerItemListEnd
        }
        \vspace{-2pt}
      \resumeItem {Project Management Tool (C\#, Silverlight, ASP.NET)}
          {\resumeInnerItemListStart
            \resumePoint{A Multi-tenant SaaS application having about 2000 tenants and 2000-5000 users per tenant.}
            \resumePoint {Spearheaded the re-architecture of the legacy application. Also increased the test coverage from 16\% to 65\%.}
            \resumePoint {Optimized complex SQL queries to improve the performance of key features by around 80\%.}
          \resumeInnerItemListEnd}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Achievements}
  \resumeSubHeadingListStart
    \resumePoint{'Best Research Project' award at the IEEE International Advance Computing Conference 2015, held at B.M.S College of Engineering. The project also featured in the \href{https://drive.google.com/open?id=0B0vNhKZyi8qyam1fQ3lfaE1hMkE}{\emph{newspaper(link)}} for its novel approach of implementation.}
  \resumeSubHeadingListEnd
\end{document}