%-------------------------
% Resume in Latex
% Initial Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xifthen}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.35in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \linespread{1.2}
  \item\small{
      \textbf{#1}{: #2}
    }
}

\newcommand{\resumePoint}[1]{
  \linespread{1.2}
  \item\small{#1}
}

\newcommand{\resumeExperienceSubheading}[5]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \normalfont{\small#2} - \textbf{#3}\normalfont{#4} & #5 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingExtended}[7]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 
      \vspace{2pt} \\
      \textbf{\small#3} in \textit{#4}; \textbf{#5} & \textit{\small #6} 
    \end{tabular*}
    \ifthenelse{\isempty{#7}}%
    {}% if #1 is empty
    {\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#7}
    \end{tabular*}
    }
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeInnerItemListStart}{\begin{itemize}\vspace{-1pt}}
\newcommand{\resumeInnerItemListEnd}{\end{itemize}\vspace{2pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nikhil-sulegaon/}{\Huge Nikhil Sulegaon}} & \faMapMarker \enspace 2995 Glenwood Dr APT 113 Boulder CO USA 80301\\[3pt]
   \href{https://github.com/nikhilsu}{\faGithub \enspace https://github.com/nikhilsu} & \faEnvelopeO \enspace \href{mailto:nisu8311@colorado.edu}{nisu8311@colorado.edu} \\
   \href{https://www.linkedin.com/in/nikhil-sulegaon/}{\faLinkedin \enspace https://www.linkedin.com/in/nikhil-sulegaon/} & \faPhone \enspace \href{tel:+1-720-491-9222}{+1-720-491-9222}
   
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {University of Colorado Boulder}{Boulder, CO}
      {Master of Science}{Computer Science}{GPA: 3.83/4.0}{Aug 2017 -- Present (Expected: May 2019)}
      {Relevant courses: BigData, ML, NLP, Probabilistic Models for ML, Computer Vision, and, Object Oriented Design.}
    \resumeSubheadingExtended
      {BMS College of Engineering}{Bangalore, India}
      {Bachelor of Engineering}{Information Science and Engineering}{GPA: 8.92/10.0}{Sep 2011 -- May 2015}
      {}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \setlength\itemsep{0em}
    \item{
     \textbf{Languages}{: Python, C\#, Java, Scala, Ruby, C++, C, PHP, MATLAB, and NodeJs.}
    }
    \item{
     \textbf{Frameworks}{: Tensorflow, Keras, ASP.NET, Flask, Ruby on Rails, SpringMVC, ReactJs with Redux.}
    }
    \item{
     \textbf{Databases}{: MS SQL Server, Postgres, MySQL, and MongoDB.}
    }
    \item{
     \textbf{Others}{: Spark, Kafka, Redis, AWS(Lamba, EMR, EC2), Heroku, Qubole, CI, Docker.}
    }
 \resumeSubHeadingListEnd

%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeExperienceSubheading
      {SDE Intern}{(Data Engineering)}{Expedia Inc}{, Chicago, USA}{May 2018 - Aug 2018}
      \resumeItemListStart
          \resumePoint{Productionalized a price recommendation ML algorithm using technologies like Qubole, Spark and AWS Lambda.}
          \resumePoint{Contributed to the ideation and implementation of restructuring the existing data pipeline for performance.}
      \resumeItemListEnd
    \resumeExperienceSubheading
      {Teaching Assistant}{\href{https://www.colorado.edu/cs/csci-3308-software-development-methods-and-tools}{(S/W Dev Methods \& Tools)}}{University of Colorado Boulder}{}{Sep 2017 - Present}
      \resumeItemListStart
          \resumePoint{Teaching 60 students, full stack development and deployment of applications using core Agile principles and TDD.}
          \resumePoint{Training students on technologies like Shell Scripting, HTML/CSS, JS, Git, REST, MySQL, PHP, CI, and Heroku.}
      \resumeItemListEnd
    \resumeExperienceSubheading
      {Application Developer}{}{ThoughtWorks}{, Bangalore, India}{Aug 2015 - Aug 2017}
      \resumeItemListStart
      \resumeItem {Project Management Tool (C\#, Silverlight, ASP.NET)}
          {A Multi-tenant SaaS application having about 2000 tenants and 2000-5000 users per tenant.
          \resumeInnerItemListStart
            \resumePoint {Spearheaded the re-architecture of the legacy application using Test Driven Development for scale.}
            \resumePoint {Refactored the code base by introducing design patterns. Also increased the test coverage from 16\% to 65\%.}
            \resumePoint {Optimized complex SQL queries to improve the performance of key features by around 80\%.}
          \resumeInnerItemListEnd}
        \resumeItem {Food-Supplies Management (Python, Sklearn, Keras)}{A stock management tool to help the pantry of the office plan the supply of fruits, vegetables, and grocery in order to minimize wastage of food.}
      \resumeItem {Danglay (Ruby, Ruby on Rails)}{A scalable carpooling web application using Ruby on Rails to solve the problem of commute faced by numerous employees at ThoughtWorks.}
      \resumeItemListEnd
    \resumeExperienceSubheading
      {Freelancer}{(Embedded System Prototyping)}{Self Employed}{, Bangalore, India}{Oct 2014 - June 2015}
      \resumeItemListStart
          \resumeItem{EMG Controlled Wheelchair (Arduino, C)}{A wheelchair which was controlled by an electromyograph, aimed at helping paraplegic patients move around. This system could also be controlled by a voice recognition unit.}
          \resumeItem{Surveillance System (Java, Android, Python, C)}{Security system that enabled the owner to control the entrance gates and lockdown the house. This system also provided live surveillance of the house on a smart-phone.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{SparkBusters (Java, Spark, Kafka, Redis)}
      {A big-data project that performed Opinion mining on tweets of a commercial product. These opinions were visualized on a Map based on the sentiment score. \textbf{Links:}
      \href{https://drive.google.com/file/d/1zUeC4FPc74mw2Z6SB1qXauo8p6Ex2Cc9/view?usp=sharing}{\textit{Demo}},  \href{https://github.com/nikhilsu/SparkBusters}{\textit{GitHub}}.}
    \resumeSubItem{Object 3D Pose Estimation (Python, Tensorflow, C\#, Unity)}
      {Using a Convolutional Neural Network to predict an object\rq s 3D pose to generate real and virtual object interactions in a Hololens. \textbf{Links:}
      \href{https://drive.google.com/file/d/1kCepKQxR73tUTLuvmd1YL3sIbj1GxDdc/view?usp=sharing}{\textit{Demo}}, \href{https://drive.google.com/file/d/1mRwSJ8p2-g-gtBGl1A8seRB8SojWQphm/view?usp=sharing}{\textit{Paper}}, \href{https://github.com/nikhilsu/Object-location-detection}{\textit{GitHub}}.}
    \resumeSubItem{Agile board (Java, SpringMVC)}
      {A web based Agile board developed for an OOP-design cum refactoring exercise. Devised a \href{https://github.com/nikhilsu/Agile-board/blob/master/src/main/java/com/prorg/helper/result/Response.java}{\emph{custom design pattern}} as part of the project implementation. \textbf{Links:}
      \href{https://prorg.herokuapp.com}{\textit{App}}, \href{https://github.com/nikhilsu/Agile-board}{\textit{GitHub}}.}
    \resumeSubItem{Navisys (Java, Android, Python, C++, OpenCV)}
      {An embedded system fitted into a jacket that provides turn-by-turn navigation with human and obstacle detection to the visually impaired. \textbf{Links:}
      \href{https://drive.google.com/file/d/1bFHeZ7-7uwZ0spir3YQ7r0maWdLteEtu/view?usp=sharing}{\textit{Report}},
      \href{https://drive.google.com/file/d/1JWB67U2jjTG7cXZFVjRPVGKsv-rRhgUQ/view?usp=sharing}{\textit{Synopsis}}.}
    \resumeSubItem{\href{https://www.dropbox.com/s/grnct56cpmsiw6c/20160208_234825.mp4?dl=0}{Teacher\rq s cube (Python, Bash)}}
      {Electronic mnemonic cubes, representing alphabets of a language, that pronounced the word formed when arranged one beside the other. Aimed to help dyslexic children formulate and pronounce words.}
    \resumeSubHeadingListEnd

\vspace{5pt}
\section{Achievements}
  \resumeSubHeadingListStart
    \resumePoint{'Outstanding Teaching Assistant' award for having the best Faculty Course Questionnaire(FCQ) scores in the Computer Science department of the University of Colorado Boulder for the academic year 2017-2018.}
    \resumePoint{'Best Research Project' award at the IEEE International Advance Computing Conference 2015, held at B.M.S College of Engineering. The project also featured in the \href{https://drive.google.com/open?id=0B0vNhKZyi8qyam1fQ3lfaE1hMkE}{\emph{newspaper(link)}} for its novel approach of implementation.}
  \resumeSubHeadingListEnd
\end{document}